Notes from the President

### 2017-03-19 pnsac/newsletter/article_PresReport.tex
Incorporating latest changes after review of DRAFT #3.

The last NStar Chronicle was published in June 2016 and since that time we have
continued our work on the aircraft, but at a greatly reduced pace. Last summer
the Museum staged a Star Trek event in the Reserve Hanger which affected our
ability to work on the North Star. We were not asked to suspend our work until
the end of September, unlike in 2014 when preparations for the Star Wars event
were being made. This helped us retain our Restoration volunteers and recruit
two new ones.

At the end of September, Mike Irvin, the Museum's Conservation Special Projects
Manager, retired and we were asked to suspend work on the aircraft until a new
manager was appointed. In January, R\'{e}jean (Rej) Demers was appointed as the new
Special Projects Manager. Our work on the aircraft resumed on January 30th.

@@

I will conclude with an invitation to any of our members not volunteering at
present to come and join us. Although we have a limit on the number of
volunteers who can get their hands dirty working on restoration, we always
welcome others who would like to join us at our events. You will meet other
likeminded people and have an interesting time talking to members of the public.
You do not need to be an expert on aviation or on the North Star to contribute.
You can contact me by email at the address at the end of this newsletter if you
would like to find out more about volunteering.

>>>>

The last NStar Chronicle was published in March 2016 and since that time we have
continued our work on the aircraft, but at a greatly reduced pace. Last summer
the Museum staged a Star Trek event in the Reserve Hanger which affected our
ability to work on the North Star. We were not asked to suspend our work until
the end of September, unlike in 2014 when preparations for the Star Wars event
were being made.

At the end of September 2016, Mike Irvin, the Museum's Conservation Special Projects
Manager, retired and we were asked to suspend work on the aircraft until a new
manager was appointed. In January, R\'{e}jean (Rej) Demers was appointed as the new
Special Projects Manager. Our work on the aircraft resumed on January 30th.

@@

The Annual General Meeting of the Association was held on March 11, 2017 at the 
Museum. It was gratifying to see a good turnout of members, given the difficult
times our organization has gone through in the past few years. Both the Museum's 
Volunteer Coordinator, Cedric St. Amour, and the new Special Projects Manager 
R\'{e}jean Demers gave up their Saturday mornings to come and address our members. 
Their presentations were very well received and are further evidence of a new 
era in our relationship with the Museum.

I will conclude with an invitation to any of our members not volunteering at
present to come and join us. Although we have a limit on the number of
volunteers who can get their hands dirty working on restoration, our organization 
needs  volunteers to assist with other Association activities including merchandise
sales, special events, fund raising, communications and administrative work. Whether
you are working on the plane or doing other Association work you will meet likeminded
people and have the opportunity to speak to the general public. You do not need to 
be an expert on aviation or on the North Star to contribute. You can contact me by 
email at the address at the end of this newsletter if you would like to find out 
more about volunteering.
